---
title: "Assignment"
output: html_notebook
---

Question 1

R Theory: pnorm calculates the CDF, Dnorm calculates the pdf, qnorm performs lookup with invesrse cdf

dnorm - not very useful unless we are dealing with discrete binomials
runif is useful to get a random variable between o and 1

NB Density plots - better way to see distribution than historgram!!
```{r}
sample_y<-runif(100000)
inverse<-qexp(sample_y,5)
hist(inverse, prob=T, main="Histogram", breaks=50)
lrange<-seq(from=0,to=2,length.out = 1000)
lines(lrange, dexp(lrange,5), col="red")
mean(inverse)
var(inverse)
1/(5^2)
?pnorm
?optimize

?optim

```
Noiiice!!

Question 2

```{r}
norm_domain<-seq(from=-5,to=5,length.out=10000)
x<-dnorm(norm_domain)
ynew<-runif(10000,0,m)
xnew<-runif(10000,-5,5)
par(mfrow=c(2,2), mar=c(3,2,2,2)) 
keep<-dnorm(xnew)>ynew
plot(norm_domain, x, type = "l")
points(xnew[keep],ynew[keep],cex=.3)
```

Question 3

Sampling from Gamma distribution. We need the max of the density function

```{r}

gam_vec<-seq(-10,20,length.out=10000)
gammfunc<-dgamma(gam_vec,10,2)

plot(gam_vec,gammfunc, type = "l", col="green")
#Now we need the max of the density 

hx<-function(x,a,b){
  (a-1)*log(x)-b*x
}
fit<-optim(5,fn=hx,method = "Brent",a=10,b=2,control=list(fnscale=-1),lower=0.0001, upper = 5)
hx(fit$par,10,2)
ygam<-runif(10000,-100,hx(fit$par,10,2))
xgam<-runif(10000,-10,20)
keep_gam<-hx(xgam,10,2)>ygam

sum(keep_gam, na.rm=TRUE)
hvalues<-hx(gam_vec,10,2)
plot(gam_vec,hvalues, type = "l", col="blue", main="Yunishas Graph", xlab="Yuni's, ylab = "Yunis bumz",col="green")
points(xgam[keep_gam],ygam[keep_gam], cex=0.3)
plotted
```

Question 4: Regression

Simulate a straight line with errors.

```{r}
set.seed(1)
s<-0.25
a<--5; b<-1
x<-runif(50)
?rnorm
e<-rnorm(50, sd=s)
y<-a+b*x+e
plot(y,x)
```


Remember optmimisation using 2 inputs - use a parameter vector
```{r}
l<-function(par, x, y){
  sum((y - par[1] - par[2]*x)^2)
}

x2<-runif(500)
y2<-5+3*(x2)*4*(x2^2)
y2
plot(y2,x2)
?optim
optim(c(1,1), l, x=x, y=y)

testMatrix = matrix(c(5,5,5,5), nrow = 2, ncol=2)
rm(list = ls())

#Now a more complex one with squares - what does he want us to do for simulate??
```

Now back to the question. Using a matrix model - WHAT THE FUCK???

```{r}
test= rep(1, 100)
testvalues=runif(100)
X = cbind(test, testvalues)
parvec<-matrix(c(-5,1),nrow=2,ncol = 1)

set.seed(1)
e<-matrix(rnorm(100, sd=0.25),nrow = 100,ncol = 1)
e
Y = X%*%parvec

l2vec<-function(parvec, X, Y){
  (t(Y-X%*%parvec))%*%(Y-X%*%parvec)
}

optim(c(-1,1), l2vec, X=X, Y=Y)


?optim
```
Linear regression function
```{r}
?lm
lm(y~x)
fit_reg<-lm(y~x)
summary(fit_reg)
```

