---
title: "Loops Notebook"
output: html_notebook
---
The following segment runs a loop to calculate the weekly revenue

```{r, echo = TRUE}
setwd('/Users/Prinpillay/R_scripts')
filename<-paste("doughnuts.csv", sep="")
dn<-read.csv(filename, header=TRUE)
sumtotal<-matrix(0,nrow=100, ncol=1)
names(dn)
for (i in 1:100)
{
  for (j in 1:5)
  {
    sumtotal[i]<-sumtotal[i] + dn[i,j]
  }
}
sumtotal
```

Another way to do this is using the apply function. Rather use apply and avoid loops.

```{r, echo=TRUE}
apply(dn, 1, sum)
apply(dn, 2, sum)
```

Lists
Matrices must by default have 2 dimensions. However, arrays can be 3 dimensional. If you use a function, you need to use a list if you want to return multiple things

```{r,}
list1<-list(NULL)
list1[[1]]<-matrix(1:4, ncol=2)
list1[[2]]<-matrix(1:9, ncol=3)
lapply(list1, mean)
apply(list1[[1]],1, mean)
list
for (i in 1:2)
{
  test<-apply(list1[[i]],1, mean)
  test
}
lapply(list1, function(x) apply(x,1,mean))

```
NB Read up on function(x), lapply linking to apply!! better way than using loops
Apply = matrix
Sapply - evaluates for a vector 
Lapply for lists
```{r}
y<-1:5
fx<-function(x){ x+1 }
sapply(y, FUN=fx)
```

Rnorm - normal distribution - generator

```{r}
replicate(4, rnorm(3))
```









