---
title: "Monte Carlo Methods"
output: html_notebook
---

Calculate the expected value of the square of the values from normal dist with rate parameter of 5. Use probability density. Ie. Integral of x^2f(x), where X is an exponential distribution with lambda =5.

```{r}

```



```{r}
nsamp<-10000 #number samples drawn
x<-(rexp(nsamp,5))^2 #sample from Exp(rate=5)
hist(x, prob=TRUE) #plot histogram
mean(x)
?rexp
```

Use integrate command

```{r}
hx<-function(x){
  (x^2)*5*exp(-5*x)
}

integrate (hx, lower=0, upper=Inf)
```

lambda must be 5

```{r}
#Loop version
meanValues<-0
iValues<-0
for (i in 1:4999) {
  meanValues<-c(meanValues, mean(rexp(i, 5)))
  iValues<-c(iValues, i)
}
plot(1:5000, meanValues, type="l")

#Non-loop version
n_sizes<-seq(from=5, by=15, length.out=500)
applyMat<-matrix(n_sizes, nrow=length(n_sizes))
nonLoopMeans<-apply(applyMat,1, function(x) mean(rexp(x,5)))
nonLoopMeans
plot(n_sizes, nonLoopMeans, type="l")

```

```{r, echo=true}
meanValues2<-0
for (i in 1:5000){
  x4 <- mean(rexp(5,5))
  meanValues2<-c(meanValues,x4)
}

nsize<-c(5,10,50,1000)
par(mfrow=c(2,2))

for (i in 1:4){
  means_sample<-replicate(5000, mean(rexp(nsize[i],5)))
  hist(means_sample, prob = T) 
}
```

Assignment questions - Post a long question to do over weekend! Use Monte Carlo Sim 

X1 = 1, X2 = mean of random dist. 

Expected Value = Do something many times - simulate 10000 times, different values then avaerage.

NB Dont confuse the Ns!!!! First N is normal distribution

```{r}

for (i in 1:sample(1:20,1)){
   Sum<-c(Sum,abs(rnorm(Sum[i])))
}

Sum
```

